---
title: "Caffeine Consumption - Life of a Busy College Student"
---

During the last month and a half I have recorded the amount of caffeine that I, a full time college senior and part-time student worker, has consumed. I have included the potential variables of whether or not I have homework or an exam due, how many classes I had, if I worked out that day, my wake up time, along with hours slept.

The primary predictor variable that I chose to analyze was whether homework or an exam was due that day, with the response variable being the caffeine intake in mg.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Load libraries
library(tidyverse)

# Load and clean data
data <- read_csv("data_trial_june1st")

clean_data <- data |>
  filter(!is.na(`Caffeine (mg)`), !is.na(`HW/Exam Due`)) |>
  select(`HW/Exam Due`, `Caffeine (mg)`)

# Summarize mean caffeine consumption
caffeine_summary <- clean_data |>
  group_by(`HW/Exam Due`) |>
  summarize(mean_caffeine = mean(`Caffeine (mg)`), .groups = "drop")

# Perform Welch Two Sample t-test
t_test_result <- t.test(`Caffeine (mg)` ~ `HW/Exam Due`, data = clean_data)

# Create summary table
summary_table <- tibble(
  `Test` = "Welch Two Sample t-test",
  `p-value` = signif(t_test_result$p.value, 4),
  `t-statistic` = round(t_test_result$statistic, 3),
  `Degrees of Freedom` = round(t_test_result$parameter, 2),
  `Confidence Interval` = paste0("[", round(t_test_result$conf.int[1], 2), ", ", round(t_test_result$conf.int[2], 2), "]")
)
```

::::: columns
::: {.column width="55%"}
```{r echo=FALSE, warning=FALSE}
# Plot caffeine data
ggplot(clean_data, aes(x = `HW/Exam Due`, y = `Caffeine (mg)`, color = `HW/Exam Due`)) +
  geom_jitter(width = 0.2, size = 2, alpha = 0.7) +
  stat_summary(fun = mean, geom = "crossbar", width = 0.5, fatten = 2, color = "black") +
  scale_color_manual(values = c("YES" = "brown1", "NO" = "darkgreen")) +
  scale_y_continuous(limits = c(0, 400), breaks = seq(0, 400, 50)) +
  labs(
    title = "Caffeine Consumed on Days With/Without HW/Exams",
    x = "Homework or Exam Due?",
    y = "Caffeine Intake (mg)", 
    caption = "Daily caffeine intake (mg) on days with or without homework/exams due. Each point \n on the plot represents a day's caffeine intake. Horizontal black bars \n show mean intake for each category."
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", hjust = 0.5, size = 12),
    plot.caption = element_text(size = 10, hjust = 0, margin = margin(t = 10))
  )
```
:::

::: {.column width="45%"}
```{r echo=FALSE}
# Display table
knitr::kable(summary_table, caption = "Table 1. Summary of Welch t-test comparing caffeine intake.")
```
:::
:::::
